Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-07-18 paper4.tex
20160718

\author[1]{Zhiqiang Ma}
\author[1]{Guanghui Sun}
\author[1]{Zhengkai Li}

\affil[1]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email. Email: guanghuisun@hit.edu.cn}
%\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}
%\affil[2]{Third affiliation address}

@@

In this section, the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively, the designer parameters of which are listed in Table \ref{tab:1}.\par
\begin{table}[!hbp]
\caption{Designer parameters}\label{tab:1}
\begin{center}
\begin{tabular}{ccccc}
\hline
 &S-SMC &ST-SMC &QST-SMC \\
\hline
$\delta$    & 1.1   & 1.1   & 1.1  \\
$\varphi$  & $1\times 10^{-3}$ & $1\times 10^{-3}$& $1\times 10^{-3}$ \\
$\gamma$    & 10    & 0.1     & 0.1     \\
$K_d(K_{*})$       & 1     & 1     & 1   \\
$\alpha$    & 0.8     & 0.8     & 1.2   \\
$\hat\alpha$ & *    & 0.6   & *      \\
\hline
\end{tabular}
\end{center}
\end{table}

>>>>

\author[2]{Zhiqiang Ma}
\author[1]{Guanghui Sun}
\author[2]{Zhengkai Li}

\affil[1]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email. Email: guanghuisun@hit.edu.cn}
\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China, with corresponding author email.}
%\affil[2]{Research Institute of Intelligent Control and Systems, Harbin Institute of Technology, Harbin 150001, China}
%\affil[2]{Third affiliation address}

@@

In this section, the simulations of the regulation of the deployment dynamics with saturated sliding mode control, saturated terminal sliding mode control and quasi-saturated terminal sliding mode control, and for clarity, these controllers are abbreviated as S-SMC, ST-SMC and QSF-SMC, respectively. The parameters of these controllers can selected as follows: $\delta=1.1$, $\varphi= 1\times 10^{-3}$, $\alpha = 0.8$, $K_d(K_{*})=1$, $\gamma = 0.1$ and $\hat\alpha=0.6$.\par
